CRUSE to Safe Cycling in Ireland

### 2023-09-13 paper.qmd
Update paper
Simplify website
Add links to REF ICSs

Commute and school travel

Other trip purposes

@@

# References {.unnumbered}

>>>>

Commute and school travel.

The methods used to generate the evidence presented in the CRUSE tool for Ireland build on previous work, particularly the Propensity to Cycle Tool (PCT), which was originally developed for the UK's Department for Transport and which is publicly available at www.pct.bike [@lovelace2017].
The original PCT has had major policy impacts.
It has "revolutionised strategic cycle planning in England and Wales"^[
See REF Impact Case Study "Cycle network policy, planning and investment transformed by the Propensity to Cycle Tool" at [results2021.ref.ac.uk](https://results2021.ref.ac.uk/impact/847d1191-7f25-46ba-a399-b481125edc8f) submitted by the University of Leeds.
]
by overcoming the barriers to cycling investment imposed by lack of evidence on cycling potential^[
See the REF Impact Case Study "Creating Step Changes in Cycling Policy and Infrastructure Planning across the UK" at [results2021.ref.ac.uk](https://results2021.ref.ac.uk/impact/4BBF3436-FD10-4C75-9791-F5E98AB4411B) submitted by the University of Westminster.
]

@@
